%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Abhilash Knox George}{ \urlstyle{same}\href{https://www.abhilashkgeorge.com}{www.abhilashkgeorge.com} | \href{https://www.linkedin.com/in/abhilashkgeorge}{LinkedIn} | \href{mailto:abhilashkgeorge@gmail.com}{user.abhilash@gmail.com} | +91 7624842110}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{KVG College of Engineering}
\descript{B.E, Computer Science}
\location{Feb 2021 | Sullia}
GPA: 7.8
\sectionsep

\subsection{St. Aloysius P U College}
\descript{Pre University, Electronics And Communication}
\location{Apr 2017 | Mangalore}
GPA: 8.0
\sectionsep

\subsection{Indraprastha Vidyalaya}
\descript{High School}
\location{Mar 2015 | Uppinangady}
GPA: 8.9
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/abhilashkgeorge}{\bf abhilashknoxgeorge} \\
Website://  \href{https://www.abhilashkgeorge.com}{\bf www.abhilashkgeorge.com} \\
GitHub:// \href{https://github.com/abhilashkgeorge}{\bf abhilashkgeorge} \\
Twitter:// \href{https://twitter.com/AbsKgeorge}{\bf AbhilashKGeorge} \\
Replit:// \href{https://replit.com/@abhilashkgeorge}{\bf abhilashkgeorge} \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{} Swift (SwiftUI, UIKit) \textbullet{} Python \textbullet{} Java \\
\textbullet{} JavaScript \textbullet{} TypeScript \textbullet{} C \textbullet{} C++ \\
\textbullet{} Assembly \textbullet{} Angular \textbullet{} Ionic \textbullet{} Cordova \\
\textbullet{} HTML \textbullet{} CSS \\
\sectionsep

\subsection{Tools}
\textbullet{} Git \textbullet{} XCode \textbullet{} Android Studio \\
\textbullet{} NodeJS \textbullet{} MongoDB \textbullet{} SQL \\
\textbullet{} REST API \textbullet{} Ionic Hybrid Development \\
\textbullet{} Adobe Creative Cloud \textbullet{} moodle \\
\textbullet{}  Unix/Linux system administration \\
\sectionsep

\subsection{Architectural Patterns}
\textbullet{} MVVM  \textbullet{} MVC \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
\textbullet{} Unix Tools and Scripting \\
\textbullet{} Operating Systems \\
\textbullet{} Advanced Machine Learning \\
\textbullet{} Computer Graphics + Practicum \\
\textbullet{} Artificial Intelligence + Practicum \\
\textbullet{} Cloud Computing \\
\textbullet{} Defending Computer Networks \\
\textbullet{} Automata, Computability, and Complexity \\
\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Robosoft Technology Pvt Ltd}
\descript{| iOS Developer }
\location{Aug 2021 - Present | Karnataka, India}
\sectionsep
\begin{tightemize}
\item Presently working on a project for \location{Tanishq iOS App} using Swift and UIKit.  \href{https://apps.apple.com/in/app/tanishq-a-tata-product/id1494086207}{\bf {\footnotesize \textit{\textbf{(AppStore Link) }}}}
\item Worked on a team for a  customer engagement application named \location{Capitastar} using Swift and UIKit. \href{https://apps.apple.com/in/app/capitastar-work-india/id1565264581}{\bf {\footnotesize \textit{\textbf{(AppStore Link) }}}}
\item Led a team of 52 as a part of Technical Intern Training Program.
\item Worked as a team for \location{World of Titan App} using version control and software like Jira, GitHub and SourceTree.
\href{https://apps.apple.com/in/app/titan-world/id1351637761}{\bf {\footnotesize \textit{\textbf{(Link) }}}}
\end{tightemize}
\sectionsep

\runsubsection{Yesen Energia Private Limited}
\descript{| Website/Application Developer [Freelancing] }
\location{Jun 2020 - Aug 2021 | Kerala, India}
\begin{tightemize}
\item Developed and published a digital learning application "goscore App" on both Play Store and App Store using Ionic framework and Moodle. \href{https://apps.apple.com/in/app/goscore-app/id1608910579?uo=2}{\bf {\footnotesize \textit{\textbf{(AppStore Link) }}}}
\item Created an E-commerce site "www.goscoreweb.com" for buying courses and launched an E-learning website "class.goscoreweb.com" for students to access the bought courses.  \href{https://class.goscoreweb.com/}{\bf {\footnotesize \textit{\textbf{(LMS Link) }}}}
\item Hosted and maintained the server associated with the apps and websites.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\subsection{Haldirams's LMS} 
 \textbullet{} Developed and published Android and iOS app for Haldiram. \href{https://play.google.com/store/apps/details?id=com.abhilashkgeorge.haldiram&pli=1}{\bf {\footnotesize \textit{\textbf{(Playstore Link) }}}} \\
 \location{Technology: \textbullet{} Ionic Framework \textbullet{} Cordova
 \textbullet{} JavaScript \textbullet{} Angular \textbullet{} HTML+ CSS } 
 \sectionsep

\subsection{EduSkills}
\textbullet{} Developing, publishing, and maintaining Web, Android and iOS apps. \href{https://play.google.com/store/apps/details?id=com.abhilashkgeorge.eduskills}{\bf {\footnotesize \textit{\textbf{(PlayStore Link) }}}} \\
 \location{Technology: \textbullet{} Cordova \textbullet{} Node
 \textbullet{} JavaScript \textbullet{} Postman \textbullet{} Moodle Development } 
\sectionsep

\subsection{Custom Android OS for Students}
\textbullet{} Developed features and functionalities that enhance the student experience and productivity and are tailored to the needs of students. \\
 \location{Technology: \textbullet{} Java  \textbullet{} Bash Scripting  \textbullet{} Makefiles  \textbullet{} ADB  }
\sectionsep

\subsection{DBMS Project - Clinical Management System}
\textbullet{} Explored the data management system followed in clinics. \\
 \location{Technology: \textbullet{} MYSQL  \textbullet{} Java
 \textbullet{} Apache Tomcat  } 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERNSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internships}

\runsubsection{Robosoft Technology Pvt Ltd}:
\location{12 Months} 
\textbullet{} iOS app development \textbullet{} JS \textbullet{} TS \textbullet{} NodeJS \textbullet{} MongoDB. \\
\sectionsep
\runsubsection{Kaggle}:
\location{2 Months} 
Internship on "PYTHON COMPLETE COURSE". \\
\sectionsep
\runsubsection{Android App Development Internship}:
\location{6 Months} 
Native Android App Development using Java. \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}

\textbullet{} Intermediate Machine Learning from Kaggle \\
\textbullet{} Python Certification from Google \\
\textbullet{} Cyber Security Certification using Kali Linux \\
\sectionsep

\end{minipage} 
\end{document}

